A pipeline to analyse time-course gene expression data

### 2020-10-08 scripts/manuscript.Rmd
Switch to plain old pdf_document
Adding OSF link

keywords: >
    time-course gene expression data, clustering, differential expression,
    workflow
vignette: >
    %\VignetteIndexEntry{A worfklow for low-level analyses of scRNA-seq data}
    %\VignetteEngine{knitr::rmarkdown}
header-includes:
   - \usepackage{float}
output: rticles::arxiv_article
bibliography: bibliography.bib
always_allow_html: yes
---

@@

The source code for this workflow can be found at
[https://github.com/NelleV/2019timecourse-rnaseq-pipeline](https://github.com/NelleV/2019timecourse-rnaseq-pipeline).
Archived source code at the time of publication can be found at [XXX](XXX).

>>>>

keywords: >
    time-course gene expression data, clustering, differential expression,
    workflow
vignette: >
    %\VignetteIndexEntry{A worfklow for low-level analyses of scRNA-seq data}
    %\VignetteEngine{knitr::rmarkdown}
header-includes:
   - \usepackage{float}
output: pdf_document
bibliography: bibliography.bib
always_allow_html: yes
---

@@

The source code for this workflow can be found at
[https://github.com/NelleV/2019timecourse-rnaseq-pipeline](https://github.com/NelleV/2019timecourse-rnaseq-pipeline).
Archived source code at the time of publication can be found at [https://osf.io/2a5tw/](https://osf.io/2a5tw/).
